Flexible Scientific Data Management for Plant Phenomics Research

### 2013-04-15 s4biodiv2013/PODD-S4BIODIV-Submission.tex
rewrite Section 2.2 based on review

\subsection{Redesign of the Phenomics Ontology Driven Data repository}
The PODD repository relies on semantic web technologies to
manage phenomics data and metadata. Although both ontologies and mappings are
essential, in PODD it was necessary to build the system with a relaxed
ontological vocabulary to allow scientists to generate datasets before they were
certain about the semantic meaning of their work. In addition, it was necessary
for PODD to allow scientists to continue to maintain projects containing curated
scientific concepts alongside raw experimental data. The PODD repository was 
redesigned based on an evaluation of the original software \cite{Li2010} that 
found it was not able to scale sufficiently to suit the HRPPC needs. The 
major differences to the software implemented by \cite{Li2010} are that projects 
are no longer the only supported top object type, and projects are not stored 
in multiple parts, as that approach was not able to scale as was originally hypothesised.

>>>>

\subsection{Redesign of the Phenomics Ontology Driven Data repository}
The PODD repository relies on semantic web technologies to
manage phenomics data and metadata. Although both ontologies and mappings are
essential, in PODD it was necessary to build the system with a relaxed
ontological vocabulary. This enables scientists to sparsely populate their datasets 
and sparsely link to community defined upper ontologies as necessary. This 
allows scientists to continue to maintain projects containing curated
scientific concepts alongside raw experimental data. The PODD repository was 
redesigned based on an evaluation of the original software \cite{Li2010} that 
found it was not able to scale sufficiently to suit the HRPPC needs due to design 
and implementation deficiencies. The major differences to the software implemented 
by \cite{Li2010} are that projects are no longer the only supported top object type, 
and projects are not stored in multiple parts, as that approach was not able to 
scale as was originally hypothesised.
